Example Manuscript Template for a Data Analysis Project

### 2023-02-09 products/manuscript/Manuscript.qmd
Updated with here() command

## Picnic Table Data 
```{r}
library(readxl)
PTD<- read_excel("C:/GitHub/MADA/KimberlyPerez-MADA-project/data/raw_data/Picnic_Table_Data.xlsx")
View(PTD)
summary(PTD)
```
## Feeder Data
```{r}
library(readcsv)
FD<- read.csv("C:/GitHub/MADA/KimberlyPerez-MADA-project/data/raw_data/Feeder Data.csv")
View(FD)
summary(FD)
```

>>>>

## Picnic Table Data 
```{r}
library(readxl)
PTD<- read_excel(here("data", "raw_data", "Picnic_Table_Data.xlsx"))
View(PTD)
summary(PTD)
```
## Feeder Data
```{r}
library(readcsv)
FD<- read.csv(here("data", "raw_data", "Feeder Data.csv"))
View(FD)
summary(FD)
```
